---
title: "Systematic Literature Review with quantitative analysis of scientific production: Scientometrics using R"
author: "Randy Quindai"
date: "August, 2018"
output: 
  html_document:
    toc: true
    fig_caption: true
    df_print: paged
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*LaCCAN, Brasil | *
*Federal University of Alagoas*

## Introduction
The project associated to this document can be found on github  at <https://github.com/SensorNet-UFAL/slrqqanalysis>, we are accepting pull requests, please feel free to send us yours recommendations.
All data was tested in this configuration settings:
```{r}
sessionInfo()
```

## Reading Data {.tabset .tabset-fade}

### Bibtex 
There are many ways to read bibtex data in R, we'll list all the different methods we can find out there, or propose new ones.

**Bibliometrix** is the library used in this snippet, *savedrecs.bib* is the bibtex file extracted.
```{r bibliometrix, message=FALSE, warning=FALSE}
library(bibliometrix)
D <- readFiles("savedrecs.bib")
M <- convert2df(D, dbsource = "isi", format = "bibtex")
#One can explore all the field tags imported from bib file
M
```
Based on <https://cran.r-project.org/web/packages/bibliometrix/vignettes/bibliometrix-vignette.html>, more details exploring the library bibliometrix can be found there, details of fields <http://www.bibliometrix.org/documents/Field_Tags_bibliometrix.pdf>.

### PDF
xxxx

## Processing data
Using `bibliometrix` package, below gaphic can be visualized.
```{r keyword}
NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)
```


Countries collaborating on this set of bibliographic data
```{r}
countries <- metaTagExtraction(M, Field = "AU_CO", sep = ";")
NetMatrix <- biblioNetwork(countries, analysis = "collaboration", network = "countries", sep = ";")
net=networkPlot(NetMatrix, n = dim(NetMatrix)[1], Title = "Country Collaboration", type = "circle", size=TRUE, remove.multiple=FALSE,labelsize=0.7,cluster="none")
```


One can visualize for instance, which articles cite a specific author
```{r}
M[grep("CHEONG E", M$CR),2]
```

Local citations
```{r}
localTC <- localCitations(M, sep = ";")
lapply(localTC, head)
```


Or to obtain the most dominant authors in a set
```{r}
library(bibliometrix)
results <- biblioAnalysis(M, sep = ";")
dominance(results, k=10)
```


<br/>


ID		 Keywords Plus associated by ISI or SCOPUS database
Type `help("conceptualStructure")` to see details about this function.
```{r}
library(bibliometrix)
cs <- conceptualStructure(M, field = "ID", method = "MCA", quali.supp = NULL, quanti.supp = NULL, minDegree = 2, k.max = 5, stemming = FALSE, labelsize = 10, documents = 50)
```


&nbsp;


Create a historigraphic map proposed by E. Garfield to represent a chronological network map os most relevant direct citations resulting from a bibliographic collection.
```{r}
options(width=130)
histResults <- histNetwork(M, min.citations = 10, sep = ".  ")
net <- histPlot(histResults, n=10, size = 10, labelsize=5, size.cex=TRUE, arrowsize = 0.5, color = TRUE)
```


```{r}
library(bibliometrix)
library(reshape2)
library(ggplot2)
kword <- KeywordGrowth(M, Tag = "DE", sep = ";", top = 15, cdf = TRUE)
DF = melt(kword, id='Year')
#timeline keywords ggplot
ggplot(DF,aes(x=Year,y=value, group=variable, shape=variable, colour=variable))+
  geom_point()+geom_line()+ 
  scale_shape_manual(values = 1:15)+
  labs(color="Author Keywords")+
  scale_x_continuous(breaks = seq(min(DF$Year), max(DF$Year), by = 5))+
  scale_y_continuous(breaks = seq(0, max(DF$value), by=10))+
  guides(color=guide_legend(title = "Author Keywords"), shape=FALSE)+
  labs(y="Count", variable="Author Keywords")+
  theme(text = element_text(size = 10))+
  facet_grid(variable ~ .)
```


# Extras

https://www.researchgate.net/post/What_software_do_you_recommend_for_scientometrics_studies

https://www.mindmeister.com/39583892/research-tools-by-nader-ale-ebrahim

http://www.jzus.zju.edu.cn/manuscript.php

