---
title: "Systematic Literature Review with quantitative analysis of scientific production"
author: "Randy Quindai"
date: "August, 2018"
output: 
  html_document:
    toc: true
    fig_caption: true
    df_print: paged
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*LaCCAN, Brasil | *
*Federal University of Alagoas*

## Introduction
The project associated to this document can be found on github  at <https://github.com/SensorNet-UFAL/slrqqanalysis>, we are accepting pull requests, please feel free to send us yours recommendations.
All data was tested in this configuration settings:
```{r}
sessionInfo()
```

## Reading Data {.tabset .tabset-fade}

### Bibtex 
There are many ways to read bibtex data in R, we'll list all the different methods we can find out there, or propose new ones.

**Bibliometrix** is the library used in this snippet, *savedrecs.bib* is the bibtex file extracted.
```{r bibliometrix, message=FALSE, warning=FALSE}
library(bibliometrix)
D <- readFiles("savedrecs.bib")
M <- convert2df(D, dbsource = "isi", format = "bibtex")
#One can explore all the field tags imported from bib file
M
```
Based on <https://cran.r-project.org/web/packages/bibliometrix/vignettes/bibliometrix-vignette.html>, more details exploring the library bibliometrix can be found there, details of fields <http://www.bibliometrix.org/documents/Field_Tags_bibliometrix.pdf>.

### PDF
xxxx

## Processing data
Using `bibliometrix` package, below gaphic can be visualized.
```{r keyword, echo=FALSE}
NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)
```

One can visualize for instance, which articles cite a specific author
```{r}
M[grep("CHEONG E", M$CR),2]
```

Local citations
```{r}
localTC <- localCitations(M, sep = ";")
lapply(localTC, head)
```


Or to obtain the most dominant authors in a set
```{r}
library(bibliometrix)
results <- biblioAnalysis(M, sep = ";")
dominance(results, k=10)
```

