---
title: "Systematic Literature Review with quantitative analysis of scientific production"
author: "Randy Quindai"
date: "August , 2018"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
The project associated to this document can be found on github  at <https://github.com/SensorNet-UFAL/slrqqanalysis>, we are accepting pull requests, please feel free to send us yours recommendations.
All data was tested in this configuration settings:
```{r}
sessionInfo()
```

## Reading Data

### Bibtex
There are many ways to read bibtex data in R, we'll list all the different methods we can find out there, or propose new ones.

**Bibliometrix** is the library used in this snippet, *savedrecs.bib* is the bibtex file extracted.
```{r bibliometrix, message=FALSE, warning=FALSE}
library(bibliometrix)
D <- readFiles("savedrecs.bib")
M <- convert2df(D, dbsource = "isi", format = "bibtex")
```
Based on <https://cran.r-project.org/web/packages/bibliometrix/vignettes/bibliometrix-vignette.html>

### PDF
xxxx

## Processing data


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
